\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\begin{flushright}
\textsl{Our technological powers increase, }\\
\textsl{but the side effects and potential hazards also escalate.}\\

\par\end{flushright}

\begin{flushright}
\medskip{}
 --- Arthur C, Clarke
\par\end{flushright}

\bigskip{}


\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax 


\chapter*{Acknowledgments}

First and foremost, I would like use this opportunity to thank both
of my supervisors, Prof. Dr. Pieter Hartel and Elmer Lastdrager MSc.
I am thankful for their unrelenting guidance and support, which have
made this research possible. They have gone beyond the expected duties
as supervisors and helped make this master thesis possible. They have
provided me with invaluably constructive thoughts and critical feedback.
I am sincerely grateful to them for sharing their truthful and illuminating
views on a number of issues related to the research. It was Elmer's
vision to integrate a phishing emails corpus with Cialdini's principles
as the core of my research. He has assisted me in obtaining the data
as it is confidential and sensitive. 

I would like to thank PhD candidates in the SCS group for letting
me pick their brains when I did a brief presentation at the beginning
of my research. Thanks to Geert Jan for letting me work in the lab.
and to Suse and Bertine for lending me the key when no one else was
in the lab. I would also like to express my appreciation and gratitude
to Drs. Jan Schut for providing me invaluable advice and direction
throughout my study in University of Twente. 

A special thanks to Eyla who has give me incentives to strive towards
my goal and for being there in difficult times, and Gaurav and Vignesh
who have assisted me by giving feedback on my writing. I appreciate
all my friends, Aldi, Saud and all the others who supported me either
directly and indirectly during my master studies. Without all their
support, accomplishing my studies would not have been possible. I
would like to thank my family members and relatives who have supported
me financially and emotionally throughout my entire master education.
Words cannot express how grateful I am to my mother and father in
spite of all the difficult times, I thank you all for letting me cherish
my dream. Lastly, I thank God almighty for answering my prayers.

\ 

-- \textsl{Nurul Akbar (Nolie)}

\endgroup
